---
title: "Liverpool Football Clubs Best Statistical 11"
description: |
  The in-depth rundown of Liverpool Football Club's
  players and corresponding statistics.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


library(tidyverse)
library(ggthemes)

goal_keeping <- read.csv("goal_keeping.csv", header = TRUE)
view(goal_keeping)

defensive_action <- read.csv("defensive_action.csv", header = TRUE)
view(defensive_action)

possession <- read.csv("possession.csv", header = TRUE)
view(possession)

goals_and_shot_creation <- read.csv("goals_and_shot_creation.csv", header = TRUE)
view(goals_and_shot_creation)
```

###  Goalkeeper
The first step to creating our starting eleven is the goalkeeper and arguably our most important position.  

```{r Goalkeeper wrangling and graph}

goal_keeping %>% 
select(Player, GA90) %>%
  ggplot(mapping = aes(fill = Player, y = GA90))+
geom_histogram(bins = 6, position = "dodge", color = "black") +
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank())+  
  labs(title = "Alisson is the Best Liverpool FC Goalkeeper", 
  subtitle = "Alisson lets in less goals per game on average", 
  y = "Goals Scored Against Liverpool FC Per 90 Minutes", 
  x = "", fill = "Player", caption = "Source: Liverpool Premier League Champions 19/20 Complete (2020)")
```

###  Defenders
Liverpool FC will need four defensive minded players to protect the newly selected goalkeeper Alisson.  

```{r Defenders wrangling and graph}
defensive_action %>%
select(Player, Def_3rd)%>%
  group_by(Player)%>%
  summarize(Player, Def_3rd)%>%
ggplot(mapping = aes(y = reorder(Player, +Def_3rd), x = Def_3rd, fill = Player))+
geom_col(position = "dodge", stat = "identity",  bins = 2)+
  theme_classic()+
  labs(title = "Liverpool FC's Best Back Four Based on Tackles", 
       subtitle = "The new back four consists of the top tacklers in the defensive third", 
       x = "Tackles in Defensive Third", y = "Players")
```

###  Midfielders
The heart of all teams is the midfield and Liverpool FC will need three of them.

```{r Midfielders wrangling and graph}
defensive_action %>%
select(Player, Def_3rd)%>%
  group_by(Player)%>%
  summarize(Player, Def_3rd)%>%
ggplot(mapping = aes(y = reorder(Player, +Def_3rd), x = Def_3rd, fill = Player))+
geom_col(position = "dodge", stat = "identity",  bins = 2)+
  theme_classic()+




