---
title: "Liverpool Football Club Best Statistical Eleven"
description: |
  The in-depth rundown of Liverpool Football Club players and corresponding statistics.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


library(tidyverse)
library(ggthemes)

goal_keeping <- read.csv("goal_keeping.csv", header = TRUE)
view(goal_keeping)

defensive_action <- read.csv("defensive_action.csv", header = TRUE)
view(defensive_action)

possession <- read.csv("possession.csv", header = TRUE)
view(possession)

Standard_stats <- read.csv("Standard_stats.csv", header = TRUE)
view(Standard_stats)
```

##  Goalkeeper
The first step to creating our starting eleven is the goalkeeper and arguably our most important position.  

```{r Goalkeeper wrangling and graph}

  goal_keeping %>%
select(Player, GA90)%>%
  group_by(Player)%>%
  summarize(Player, GA90)%>%
ggplot(mapping = aes(y = reorder(Player, +GA90), x = GA90, fill = Player))+
geom_col(position = "dodge")+
  theme_classic()+
  labs(title = "Alisson is the Best Liverpool FC Goalkeeper", 
  subtitle = "Alisson lets in less goals per game on average", 
  y = "Player", 
  x = "Goals Scored Against Liverpool FC Per 90 Minutes", fill = "Player", caption = "Source: https://fbref.com")
```
###  Goalkeeper: Alisson

##  Defenders
Liverpool FC will need four defensive minded players to protect the newly selected goalkeeper Alisson.  

```{r Defenders wrangling and graph}
defensive_action %>%
select(Player, Def_3rd)%>%
  group_by(Player)%>%
  summarize(Player, Def_3rd)%>%
ggplot(mapping = aes(y = reorder(Player, +Def_3rd), x = Def_3rd, fill = Player))+
geom_col(position = "dodge")+
  theme_classic()+
  labs(title = "
Liverpool FC Best Back Four Based on Tackles", 
       subtitle = "The new back four consists of the top tacklers in the defensive third", 
       x = "Tackles in Defensive Third", y = "Players", 
       caption = "Source: https://fbref.com")
```
###  Defenders: Trent Alexander-Arnold, Virgil Van Dijk, Jordan Henderson, and Fabinho


##  Midfielders
The heart of all teams is the midfield and their ability to dribble the ball, Liverpool FC will need three of them.

```{r Midfielders wrangling and graph}
possession%>%
select(Player, Succ_)%>%
  group_by(Player)%>%
  summarize(Player, Succ_)%>%
ggplot(mapping = aes(y = reorder(Player, -Succ_), x = Succ_, fill = Player))+
geom_col(position = "dodge")+
  theme_classic()+
  labs(title = "The Best Possible Middle Three For Liverpool", 
       subtitle = "The new back four consists of the best dribblers in the team", 
       x = "Percentage of Successful Take-ons", y = "Players", 
       caption = "Source: https://fbref.com")
```
###  Midfielders: Curtis Jones, Joel Matip, and Naby Keita

##  Attackers
The firepower of Liverpool FC and the goalscorers of any team. The attackers will consist of the three top scoring players in the team. 

```{r Attackerrs wrangling and graph}
Standard_stats%>%
select(Player, Gs)%>%
  group_by(Player)%>%
  summarize(Player, Gs)%>%
ggplot(mapping = aes(y = reorder(Player, +Gs), x = Gs, fill = Player))+
geom_col(position = "dodge")+
  theme_classic()+
  labs(title = "The Highest Scoring Liverpool FC Front Three", 
       subtitle = "The front three will consist of the top scorers throughout the season", 
       x = "Goals Scored or Allowed", y = "Players", 
       caption = "Source: https://fbref.com")
```

###  Attackers: Mohamed Salah, Roberto Firmino, and Sadio Mane

##  Final Eleven

Alisson,
Fabinho,   Virgil Van Dijk,   Jordan Henderson,    Trent Alexander-Arnold,
Curtis Jones,    Joel Matip,    Naby Keita,
Mohamed Salah,   Roberto Firmino,   Sadio Mane


              



